---
title: "Post-Acute Phases"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
library(pander)

```


```{r load myData, include=FALSE}
load("PostSequelaeListSIMULATED.RData")
```

## Number of Encounters
### Count of patients with a certain number of registred encounter

```{r , echo=FALSE}
plot(PostSequelaeList$NumberofEncounters)
```

## Duration and days between of Encounters
### Duration (days) of the first admission for all the subjects

```{r , echo=FALSE}
plot(PostSequelaeList$Durationofthefirstadmission)
```

### Duration (days) of the first admission, in subject with/without a second readmission

```{r , echo=FALSE}
plot(PostSequelaeList$DurationofthefirstadmissionGroups)
```

### Duration (days) of single encouters following the first admission
```{r , echo=FALSE}
plot(PostSequelaeList$DurationoftheSinglefollowingencounters)
```

### Duration (days) of the entire observation period following the first admission 

```{r , echo=FALSE}
plot(PostSequelaeList$TotalDurationofthefollowingencounters)
```



## Diagnosis
### Diagnosis in Encounters
```{r ,echo=FALSE, fig.width = 15 ,fig.asp = .62,cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE}
plot(PostSequelaeList$DiagnosisBubblePlot)
```

